`infercnv` results exploration for `r params$sample_id`

### 2024-10-28 analyses/cell-type-wilms-tumor-06/notebook_template/06_cnv_infercnv_exploration.Rmd
few changes to PR828

@@

Do_CNV_heatmap <- function(object, infercnv_obj, group.by){

@@

@@

```{r }
visualize_feature <- function(object, features, group.by ){

                  d <- SCpubr::do_FeaturePlot(object, 
                                              features = features, 
                                              pt.size = 0.2, 
                                              legend.width = 0.5, 
                                              legend.length = 5, 
                                              legend.position = "right") + ggtitle(features)
                  b <- SCpubr::do_ViolinPlot(object, 
                                             features = features, 
                                             ncol = 1, 
                                             group.by = group.by, 
                                             legend.position = "none",
                                             assay = "SCT") + ylab(features)

@@

```{r fig.width=20, fig.height=5, out.width='100%', out.height='100%'}
infercnv_obj <- list()
for(reference_value in c("reference-none", "reference-immune", "reference-endothelium", "reference-both")){
  infercnv_obj[[reference_value]] <- readRDS(file.path(result_dir, glue::glue(reference_value, "_HMM-no") , glue::glue("06_infercnv_", params$sample_id, "_", reference_value, "_HMM-no.rds")))
  print(Do_CNV_heatmap(object = srat, infercnv_obj = infercnv_obj[[reference_value]], group.by = "fetal_kidney_predicted.compartment"))
}

@@

for(reference_value in c("reference-none", "reference-immune", "reference-endothelium", "reference-both")){
  srat <- Do_CNV_score(srat,infercnv_obj = infercnv_obj[[reference_value]], reference_value)
  p1 <- visualize_feature(srat, glue::glue("CNV-score_", reference_value) , group.by = "fetal_kidney_predicted.compartment" )
  p2 <- visualize_density(srat, features=glue::glue("CNV-score_", reference_value), group.by = "fetal_kidney_predicted.compartment")
  print(p1 + p2 + plot_layout(ncol = 3, widths = c(1,2,2)))
}

@@

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat_i3, features=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment"))
}
```

@@

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat_i6, features=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment"))
}
```

@@

The selection of normal cells to be spiked-in as a normal reference prior running `infercnv` has been performed in `06a_build-normal-cell_reference.R.
We selected samples that haven't been pre-treated with chemotherapies. Indeed, even if normal cells shouldn't be affected by chemotherapy in terms of CNV, we are not sure how chemotherapies can affect the CNV profile of normal cells.
We thus decided to only take endothelial and immune cells from non-treated samples to build the reference of normal cells.

@@

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat, features=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment"))
}
```

>>>>

- `reference_value` indicates the reference used for `infercnv`, either endothelial, immune, both or pool.

@@

Do_CNV_heatmap <- function(object, infercnv_obj, group.by, reference_value){

@@

- `feature` the gene or quantitative value to be plotted

@@

```{r }
visualize_feature <- function(object, feature, group.by ){

                  d <- SCpubr::do_FeaturePlot(object, 
                                              features = feature, 
                                              pt.size = 0.2, 
                                              legend.width = 0.5, 
                                              legend.length = 5, 
                                              legend.position = "right") + ggtitle(as.character(feature))
                  b <- SCpubr::do_ViolinPlot(object, 
                                             features = feature, 
                                             ncol = 1, 
                                             group.by = group.by, 
                                             legend.position = "none",
                                             assay = "SCT") + ylab(as.character(feature))

@@

```{r fig.width=20, fig.height=5, out.width='100%', out.height='100%'}
infercnv_obj <- list()
for(reference_value in c("reference-none", "reference-immune", "reference-endothelium", "reference-both")){
  infercnv_obj[[reference_value]] <- readRDS(file.path(result_dir, glue::glue(reference_value, "_HMM-no") , glue::glue("06_infercnv_", params$sample_id, "_", reference_value, "_HMM-no.rds")))
  print(Do_CNV_heatmap(object = srat, infercnv_obj = infercnv_obj[[reference_value]], group.by = "fetal_kidney_predicted.compartment", reference_value = reference_value))
}

@@

for(reference_value in c("reference-none", "reference-immune", "reference-endothelium", "reference-both")){
  srat <- Do_CNV_score(srat,infercnv_obj = infercnv_obj[[reference_value]], reference_value)
  p1 <- visualize_feature(srat, feature =  glue::glue("CNV-score_", reference_value) , group.by = "fetal_kidney_predicted.compartment" )
  p2 <- visualize_density(srat, features=glue::glue("CNV-score_", reference_value), group.by = "fetal_kidney_predicted.compartment")
  print(p1 + p2 + plot_layout(ncol = 3, widths = c(1,2,2)))
}

@@

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat_i3, feature=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment"))
}
```

@@

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat_i6, features=c(glue::glue("proportion_cnv_chr", i)), group.by = "fetal_kidney_predicted.compartment"))
}
```

@@

The selection of normal cells to be spiked-in as a normal reference prior running `infercnv` has been performed in `06b_build-normal-cell_reference.R.
We selected samples that haven't been pre-treated with chemotherapies. Indeed, even if normal cells shouldn't be affected by chemotherapy in terms of CNV, we are not sure how chemotherapies can affect the CNV profile of normal cells.
We thus decided to only take endothelial and immune cells from non-treated samples whose label transfer scores are greater than 0.85 to build the reference of normal cells.

@@

```{r fig.width=10, fig.height=5, out.width='45%', out.height='45%'}
for(i in 1:22){
  print(visualize_feature(srat, feature=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment"))
}
```
